---
geometry: "left=2.5cm,right=2.5cm,top=3cm,bottom=3cm"
header-includes:
- \usepackage[labelformat=empty]{caption}
- \usepackage{placeins}
- \usepackage{array}
- \usepackage{float}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \usepackage{graphicx}
- \usepackage{hyperref}
- \usepackage[ddmmyyyy]{datetime}
- \usepackage{booktabs} 
- \fancyhf{}
- \fancyhead[C]{\nouppercase{\leftmark}}
- \fancyfoot[C]{\thepage}
- \fancyhead[L]{\includegraphics[height=5mm]{img/logo_eth.png}}
- \fancyhead[R]{\includegraphics[height=5mm]{img/logo_sup-bw.png}}
- \renewcommand{\headrulewidth}{0.3pt}
- \setlength{\headsep}{0.6in} 
output:
  pdf_document:
    latex_engine: lualatex
    includes: 
      before_body: frontpage.tex
    toc: yes
    toc_depth: 3
  word_document:
    toc: yes
    toc_depth: '3'
  html_document:
    df_print: paged
fontsize: 12
linkcolor: blue
mainfont: "`r Sys.getenv('FONT')`"
---



```{r, echo = FALSE, warning = FALSE, message = FALSE}
require(pacman)

p_load(readxl,knitr,pander,kableExtra,tidyverse,stringr,tinytex,systemfonts,xml2)

# sets wd to this script's location
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

```{r}


```

```{r global_options, echo=FALSE}
# Set global chunk options
knitr::opts_chunk$set(
  # Leave empty space in table if NA
  knitr.kable.NA = " ",
  # Not displaying anything except output
  echo = FALSE,
  warning = FALSE,
  message = FALSE, 
  # Display tables (and not latex code)
  results = 'asis', 
  # Setting for summary stats 
  fig.width = 10, 
  fig.height = 4
)
```

```{r}
# load additional functions
source("scripts/functions.R")
```

```{r, include = FALSE}
# Read environment file
# You have to create this in your local folder.
# It should contain your folder path, API key, survey id, etc.
# Also see Readme

# EXTRACTING INFORMATION FROM .Renviron FILE
readRenviron("./.Renviron")

FONT = Sys.getenv("FONT")

# if it's a specific Bengali font (with special characters)
# this codeblock is from a specific project and can be deleted in the future
if (FONT == "Noto Serif Bengali") {
  # additional latex packages necessary for bengali characters
  cat("
  \\usepackage{fontspec}
  \\usepackage{babel}
  \\babelprovide[import, main]{english}
  \\babelprovide[import]{bengali}
  \\babelfont{rm}{Noto Serif Bengali}
  \\babelfont[bengali]{rm}[Scale=MatchLowercase]{Noto Serif Bengali}
  ")
  
  #Font check
  is_font_installed <- any(system_fonts()$family == FONT)
  
  if (!is_font_installed) {
    stop(paste0("The font ", FONT, " is not installed. Go to the .fonts folder and install all the necessary fonts. \n"))
  } 
} 

# if it's any other font
if (FONT != "") {
  #Font check
  is_font_installed <- any(system_fonts()$family == FONT)
  
  if (!is_font_installed) {
    stop(paste0("The font ", FONT, " is not installed. Go to the .fonts folder and install all the necessary fonts. \n"))
  } 
}

# This is the output name for the excel file
CODEBOOK_XLSX_FILENAME <- Sys.getenv("CODEBOOK_XLSX_FILENAME_STEP_2")

WAVE_PREFIX = Sys.getenv("WAVE_PREFIX")

# General variable information (e.g., question type, instruction text)
meta = eval(parse(text = Sys.getenv("META")))

# German value labels (including -8 and -9)
codes_original_language = eval(parse(text = Sys.getenv("VALUE_CODES_ORIGINAL_LANGUAGE")))

# English value labels (including -8 (EN) and -9 (EN))
codes_translated_language = eval(parse(text = Sys.getenv("VALUE_CODES_TRANSLATED_LANGUAGE")))

# Missing labels
miscodes = eval(parse(text = Sys.getenv("MISSING_VALUE_CODES")))

# load language codes from environment file
ORIGINAL_LANGUAGE_CODE = Sys.getenv("ORIGINAL_LANGUAGE_CODE")
TRANSLATED_LANGUAGE_CODE = Sys.getenv("TRANSLATED_LANGUAGE_CODE")
languages <- c(ORIGINAL_LANGUAGE_CODE, TRANSLATED_LANGUAGE_CODE)

# load response data file if add sumplots is TRUE
add_sumplots = eval(parse(text = Sys.getenv("ADD_SUMPLOTS")))
if (add_sumplots) {
  load(file = Sys.getenv("RESPONSE_FILE"))
  response = eval(parse(text = Sys.getenv("RESPONSE_DATAFRAME_NAME")))
}



```

```{r, include=FALSE}

# Excel Table into R
df_meta <- read_excel(CODEBOOK_XLSX_FILENAME)

# apply remove_html to each column if the column is character based
df_meta <- data.frame(lapply(df_meta, function(column) {
  if(is.character(column)) {
    return(sapply(column, remove_html))
  } else {
    return(column)
  }
}), stringsAsFactors = FALSE, check.names = FALSE)


```


\newpage

# Labelling Scheme 

# Missing Code Scheme
If applicable, missing values are coded as follows: 

```{r,  include=TRUE, results="asis"}

#missing labels 
#upanel.meta[c(31, 30, 13:20)] %>%
#    kable("latex", col.names = NULL, booktabs = T, linesep = "") %>% 
#    kable_styling(latex_options = c("striped", "hold_position" )) %>% 
#    column_spec(2, width = "35em")

cat("\\label{missingcodes}")

cb_mistable(metadata = df_meta)
```

# Presentation of randomisation
This wave included survey experiments. Randomly defined groups received different treatments in form of information and question texts. The treatment variables display the exact information and question texts for each group. If the treatment concerns the question text of a variable, the different versions will be presented along with the corresponding variable. The following scheme is used to present the different treatments (see [Question 40](#q40) as an example): 

+ {...} indicates all treatment values belonging to one treatment variable, 
+ [...] indicates one treatment value within a treatment variable,
+ // delimits the different treatment values and can be interpreted as an exclusive OR.

Example: {[] // [state] // [company] // [Individuum]}

The control group often receives no information or a shortened question text (without additional information). The absence of an information or text is indicated with an empty field. Control group information are either recorded by a general treatment group variable or a specific treatment variable referring to the information/text. In the latter case, [ ] is used to refer to the (empty) control group value. Otherwise, { } indicates the (empty) control group value.  

# Question Types 

The given question types explain the way respondents were allowed to answer a specific question. This is, either selecting a limited (single choice) or open (multiple choice) number of response options from a given list, inserting text or numeric values in open text boxes, or showing one’s opinion via rating on a predefined continuum. The question type meta data does not result from respondents' answers, but records basic information on individual survey rounds and respondents.


\newpage


```{r}
source("scripts/assemble_codebook_pdf.R")
```















